Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-20 chapters/introduction/introduction.tex
update flow chart, change approach section

\section{Our Approach}

\begin{figure}
  \centering
  \includegraphics[width=.8\linewidth]{introduction/architecture}
  \caption{Architecture of our approach.}
  \label{fig:intro:architecture}
\end{figure}

Our approach consists of two big steps. First, we propose a general
probabilistic model to jointly estimate the geo-calibration
parameters. The key for the success of this model is to construct good
constraint functions which describe the fitness between the calibration
parameters and the images. As the second step of our approach, we
dismantle the full geo-calibration into several partial
geo-calibration tasks, each of which could provides a strong constraint
function that fits in the general model. The architecture of
our approaches refers to \figref{intro:architecture}.
%
In the end, we show that learning to geo-calibrate a camera is helpful
for high-level image feature extracting.

>>>>

\section{Main Contributions}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{introduction/architecture}
  \caption{A simplified flowchart of our approach. The algorithm
inputs (images, time and manual annotations) are fed to different
constraint models which work as constraint functions. 
The probabilistic distribution over complete geo-calibration
parameters are then simulated jointly by fusing these constraint
functions in a general model for geo-calibration.}
  \label{fig:intro:architecture}
\end{figure}

We make contributions in three main areas: 1) We proposed a general
probabilistic model to jointly estimate the geo-calibration
parameters, 2) we decompose the full geo-calibration into several
partial geo-calibration tasks, each of which provides a strong
constraint function that fits in the general model, and 3) we show
that learning to geo-calibrate a camera is helpful for high-level
image feature extraction.

The first two contributions consist of our main approach. Our
algorithm feeds inputs (images, time and manual annotations) to
different constraint models, which work as constraint functions. Then
we fuse these constraint functions to simulate the joint distribution
over the complete geo-calibration parameters. The flowchart of
our approaches refers to \figref{intro:architecture}.

Furthermore, we also explore to learning high-level
visual features and geo-calibrating cameras simultaneously.
We believe that the geo-calibration parameters are closely related to
the image representation. 
Imagine the process of a human doing geo-localization, one could
roughly guess where a photo was taken when she sees an polar bear on
an iceberg on it. In this process, learning high-level features
becomes a necessary step of abstracting visual hints to localize
the camera.
Based on this belief, we designed network to learn useful visual
features by exploiting geographic information, which provides new ways
for automatic feature learning.
